Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-02-28 ms.tex
filled in photometric calibration text

We therefore sought to achieve an empirical photometric calibration
across all mission phases accurate at the several mmag level. Our basic
strategy was to analyze repeat measurements of compact sources near the 
ecliptic poles, where WISE gathers data every $\sim$$95$ minutes throughout the 
entire mission. Specifically, our sample consists of moderately bright,
unsaturated compact sources with $|\beta| > 85^{\circ}$, and avoiding a wedge 
defined by $-90^{\circ}$$<$$\lambda$$<25^{\circ}$ to exclude the LMC. The 
positions and nominal average magnitudes of our moderately bright source
sample were drawn from the AllWISE Source Catalog, selecting sources with 
10.6 $<$ \verb|w1mpro| $<$ 13.1 and 9.2 $<$ \verb|w2mpro| $<$ 11.7 and with
\verb|w?cc_map|=0 in the band of interest.

These spatial, magnitude and flag cuts yield samples of $\sim$109,000 
($\sim$27,000) unique calibrator sources in W1 (W2). We perform aperture 
photometry using \verb|djs_phot| with a 27.5$''$ radius for each calibrator 
source in every L1b exposure in which it appears sufficiently far from the 
image boundary. This results in a catalog of $\sim$45M ($\sim$15M) W1 (W2) 
single-epoch aperture fluxes which form the basis for our derived 
time-dependent zero points. The typical calibrator source contributes 
$\gtrsim$400 epochs of photometry.

We sought a photometic calibration with time resolution of one day. 
% mention that single-epoch fluxes grouped into one-day bins
% mention that single-epoch fluxes of each source were normalized
% to the average (median?) flux measured during the All-sky phase, and 
% that the AllWISE phase zero points were taken at face value, and
% that we used the single-exp ecl pole photometry to verify that the zero point 
% was stable at the $<=1 mmag$ level of the All-sky phase of the mission

>>>>

We therefore sought to achieve an empirical relative photometric calibration
across all mission phases accurate at the several mmag level. Our basic
strategy was to analyze repeat measurements of compact sources near the 
ecliptic poles, where WISE gathers data every $\sim$$95$ minutes throughout the 
entire mission. Specifically, our sample consists of moderately bright,
unsaturated compact sources with $|\beta| > 85^{\circ}$, and avoiding a wedge 
defined by $-90^{\circ}$$<$$\lambda$$<25^{\circ}$ to exclude the LMC. The 
positions and nominal average magnitudes of our moderately bright source
sample were drawn from the AllWISE Source Catalog, selecting sources with 
10.6 $<$ \verb|w1mpro| $<$ 13.1 and 9.2 $<$ \verb|w2mpro| $<$ 11.7 and with
\verb|w?cc_map|=0 in the band of interest.

These spatial, magnitude and flag cuts yield samples of $\sim$109,000 
($\sim$27,000) unique calibrator sources in W1 (W2). We perform aperture 
photometry using \verb|djs_phot| with a 27.5$''$ radius for each calibrator 
source in every L1b exposure in which it appears sufficiently far from the 
image boundary. This results in a catalog of $\sim$45M ($\sim$15M) W1 (W2) 
single-epoch aperture fluxes (in units of DN) which form the basis for our 
derived time-dependent zero points. The typical calibrator source contributes 
$\gtrsim$400 epochs of photometry.

We sought a photometic calibration with time resolution of one day. We
grouped the photometric measurements in two ways. For each unique source,
we lumped all of its All-sky phase measurements together to obtain its median
flux (DN) in our aperture photometry system during this phase. This is
justified because the All-sky release photometric zero points are known
to be remarkably stable. Indeed, using our ecliptic pole singe-exposure 
photometry database, we were able to confirm that the All-sky phase zero point 
was stable at the $\le$2 mmag level in each band. For every aperture
flux after the All-sky phase, we calculated a gain enhancement factor
implied by that measurement relative to the appropriate sources
median All-sky phase flux. We then grouped these gain enhancement factors
into one-day bins, and quoted the median per bin as the multiplicative
change in zero point relative to the All-sky zero point. We took the 
All-sky zero points (20.752 in W1 and 19.596 in W2) at face value.
